Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra

### 2015-05-26 ms.tex
Modify usage of off-zenith pointing in Section 3
From b9b3559:
============

In ms.tex,

(*) Modify comment on usage of off-zenith pointing in Section 3

The MWA instrument configuration, EoR observing strategy, and analysis procedure applied to individual snapshots used in this study are already described in Paper~I and references therein. {\it Off-zenith} data containing the Galactic center in Paper~I was useful in demonstrating the mapping between delay spectra and sky locations, establishing primary causes of foreground contamination, and devising a technique for mitigating foreground contamination. {\it Pitchfork} signatures which result from low-level ubiquitous diffuse emission are fainter. Since Galactic plane emission, even from directions far away from the primary field of view, can potentially swamp the fainter {\it pitchfork} signatures, zenith pointings which have a maximum avoidance of the Galactic plane are preferred for this study.

>>>>

The MWA instrument configuration, EoR observing strategy, and analysis procedure applied to individual snapshots used in this study are already described in Paper~I and references therein. In that paper, we analyzed two observations -- an {\it off-zenith} pointing that included significant Galactic plane contributions and a {\it zenith} pointing in which the Galactic plane was significantly absent. The {\it off-zenith} snapshot was useful in demonstrating the mapping between delay spectra and sky locations, establishing primary causes of foreground contamination, and devising a technique for mitigating foreground contamination. {\it Pitchfork} signatures which result from low-level ubiquitous diffuse emission are fainter. Since Galactic plane emission, even from directions far away from the primary field of view, can potentially swamp the fainter {\it pitchfork} signatures, zenith pointings which have a maximum avoidance of the Galactic plane are preferred for this study.
